---
title: "UQM paper figures - academic performance"
author: "KZ"
date: "28 May 2015"
output: html_document
---

#Import, clean, transform export    
BIOL1040 and BIOM2011, 2013, Sem 1 and 2
```{r}
#clean workspace
rm(list=ls())

#packages
require(reshape2)
require(dplyr)

#functions
source("Functions to load UQM data.R")
source("UQM functions.R")
source("HelperFunctions.R")


#load data
ProjectID = read.csv("./Data Stage 1/ProjectIDs.csv")
projects()

#AcP = Ac.performance(project.num, project.names) #creates a list called AcP for the 11 reports
AcP.biol = Ac.performance(project.num[1:7], project.names.formative[1:7], "biol")
AcP.biom = Ac.performance(project.num[8:11], project.names[8:11], "biom")
FbP = Fb.provision(project.num, project.names.formative) #creates a list called FbP for the 11 reports
FbU = Fb.use(project.num, project.names.formative) #creates a list called FbU for the 11 reports
demog = Demog() #creates a list called demog for the 4 semesters

ls = AcP.biol
for (l in 1:length(ls))
  print(lapply(ls, nrow)[[l]])
  
```

#removing errors
##FbU errors  
removes huge mB4scroll value that is inconsistent with timestamps  
```{r}
FbU[[5]][which(FbU[[5]][,1] == 440572),15] = 4587 
```

##demographics errors  
removes students with duplicate rows within a single semester unit  
(all appear to have 2 values for OP)  
```{r}
ls = demog
ls.names(ls)

ls.stud.dup = NULL
for (l in 1:length(ls))
    ls.stud.dup[[l]] = filter(ls[[l]], duplicated(StudentID)) %>% select(StudentID)
ls.stud.dup

for (l in 1:length(ls))
  for (i in 1:nrow(ls.stud.dup[[l]]))
    print(ls[[l]][which(ls[[l]][,1] == ls.stud.dup[[l]][i,]),])

ls.dim(ls)
ls[[1]] = ls[[1]][-457,]
ls[[1]] = ls[[1]][-75,]
ls[[2]] = ls[[2]][-885,]
ls[[2]] = ls[[2]][-541,]
ls[[3]] = ls[[3]][-130,]
ls[[4]] = ls[[4]][-39,]

demog = ls
```


#All
converting ls to df 
```{r}

AcP.biol.df = ls.df(AcP.biol, 0)
AcP.biom.df = ls.df(AcP.biom, 7)

SubID.StudID = rbind(AcP.biol.df[,1:2], AcP.biom.df[,1:2])

FbU.df = ls.df(FbU, 0)

FbP.df = ls.df(FbP, 0)
FbP.df = rename(FbP.df, 1, "SubmissionID")
FbP.df2 = merge(FbP.df, SubID.StudID, by="SubmissionID")
FbP.df = FbP.df2[,c(1,17,2:16)]

ls = demog
df = ls[[1]]
  for (l in 2:length(ls))
  {
    df = rbind(df, ls[[l]])
  }
df = df[,c(1,18,19,6:13,15,2,5,3,17,16)]
df = rename(df, 13:14, c("course", "sem"))
demog.df = df

#summary(AcP.biol.df)

```

##AcP errors
removing unpublished submissions  
```{r}
#BIOL1040
df = AcP.biol.df
unpub = rev(which(df[,4] == "N/A"))
df[unpub[1:5],]
df = df[-unpub,]
AcP.biol.df = df

#BIOM2011
df = AcP.biom.df
unpub = rev(which(df[,4] == "N/A"))
df[unpub[1:5],]
df = df[-unpub,]
AcP.biom.df = df
```

removing incomplete cases  
```{r}
df = AcP.biol.df
#protecting the cases where methods controls are missing (not marked for R0)
table(df[,8])
length(which(is.na(df[,8])))
for (i in 1:nrow(df)) {
  if(df[i,21] == "BIOL1040Sem1Report 0") {
    df[i,8] = 100
  }
}
table(df[,8])
length(which(is.na(df[,8])))
df[which(is.na(df[,8])),c(1:9,21)]
df = df[complete.cases(df[,5:16]),]
AcP.biol.df = df

#BIOM2011
df = AcP.biom.df
df = df[complete.cases(df[,5:19]),]
AcP.biom.df = df
```

remarks
*Level 1*  
```{r}
df = AcP.biol.df
studs.remark = NULL

studs.submissions = df %>% group_by(StudentID, project) %>% tally(sort = TRUE)
table(studs.submissions$n)
filter(studs.submissions, n >= 2) 
studs.remark = filter(studs.submissions, n >= 2) # %>% select(1:4)
studs.remark[1:5,]
studs.remark = as.data.frame(studs.remark)

df2 = NULL
for (i in 1:nrow(studs.remark)) {
  df2 = rbind(df2, subset(df, StudentID == studs.remark[i,1] & project == studs.remark[i,2]))
}
df2[1:5,]

df2[,4] = as.POSIXct(df2[,4], tz = "UTC", format = "%d/%m/%y %H:%M")
df2 = df2 %>% group_by(StudentID) %>% arrange(Publish.Time)

first.sub = df2 %>% distinct(StudentID)

df3 = df2 %>% group_by(StudentID) %>% arrange(desc(Publish.Time))
remarks = df3 %>% distinct(StudentID)

df2 %>% group_by(StudentID) %>% tally() %>% arrange(desc(n))
df2[which(df2[,1] == "S8639671"),]
first.sub[which(first.sub[,1] == "S8639671"),]
remarks[which(remarks[,1] == "S8639671"),]
remarks = rbind(remarks, df2[which(df2[,2] == 3407),])
remarks = remarks %>% group_by(StudentID) %>% arrange(desc(Publish.Time))

first.sub = as.data.frame(first.sub)
remarks = as.data.frame(remarks)

remarks.subID = remarks[,2]

#df[,2] %in% remarks.subID
length(df[,2])
length(df[,2] %w/o% remarks.subID)

df.fixed = df[-rev(which(df[,2] %in% remarks.subID)),]

AcP.biol.df = df.fixed
AcP.biol.df.remarks = as.data.frame(df2)
remarks.subID.biol = remarks.subID
```
 
*Level 2*    
```{r}
df = AcP.biom.df
studs.remark = NULL

studs.submissions = df %>% group_by(StudentID, project) %>% tally(sort = TRUE)
table(studs.submissions$n)
filter(studs.submissions, n >= 2) 
studs.remark = filter(studs.submissions, n >= 2) # %>% select(1:4)
studs.remark = as.data.frame(studs.remark)

df2 = NULL
for (i in 1:nrow(studs.remark)) {
  df2 = rbind(df2, subset(df, StudentID == studs.remark[i,1] & project == studs.remark[i,2]))
}
df2[1:5,]

df2[,4] = as.POSIXct(df2[,4], tz = "UTC", format = "%d/%m/%y %H:%M")
df2 = df2 %>% group_by(StudentID) %>% arrange(Publish.Time)

first.sub = df2 %>% distinct(StudentID)

df3 = df2 %>% group_by(StudentID) %>% arrange(desc(Publish.Time))
remarks = df3 %>% distinct(StudentID)

df2 %>% group_by(StudentID) %>% tally() %>% arrange(desc(n))

first.sub = as.data.frame(first.sub)
remarks = as.data.frame(remarks)

remarks.subID = remarks[,2]

#df[,2] %in% remarks.subID
length(df[,2])
length(df[,2] %w/o% remarks.subID)

df.fixed = df[-rev(which(df[,2] %in% remarks.subID)),]

AcP.biom.df = df.fixed
AcP.biom.df.remarks = as.data.frame(df2)
remarks.subID.biom = remarks.subID

remarks.subID = c(remarks.subID.biol, remarks.subID.biom)

```


##demographics
#students who withdrew  
converting grades to categories  
```{r}
df = demog.df
col = 15
table(df[,col])
grades = as.data.frame(names(table(df[,col])))
grades[,2] = c(1,2,2,2,3,4,3,3,2,3,4,4,5,6,7,rep("withdrawn", 3))
new.col = dim(df)[2] + 1
df[,new.col] = 0
df = rename(df, new.col, "Course.Grade")
for (i in 1:nrow(df)) {
  for (j in 1:length(grades[,1])) {
    if (df[i,col] == grades[j,1])
      df[i,new.col] = grades[j,2]
    }
}
#df[1:5,15:18]
df = df[,c(1:col,new.col,16,17)]
demog.df = df
```

identifying studetns who withrew  
```{r}
df = demog.df

withdrew = filter(df, Course.Grade == "withdrawn") 
withdrew %>% group_by(course, sem) %>% tally(sort=FALSE)
studs.withdrew = as.data.frame(withdrew %>% select(StudentID, course, sem))

w = NULL
for (i in 1:nrow(studs.withdrew))
  w[i] = paste0(studs.withdrew[i,1], studs.withdrew[i,2], "Sem", studs.withdrew[i,3])
w

new.col = dim(df)[2] + 1
df[,new.col] = 0
df = rename(df, new.col, "UniqueID")
for (i in 1:nrow(df)) {
      df[i,new.col] = paste0(df[i,1], df[i,13], "Sem", df[i,14])
}


#df2 = df[(df[,19] %w/o% w),]
#df2 = df[-(df[,19] %in% w),]
demog.wo.withrawn = df[-rev(which(df[,19] %in% w)),]

```

finding withrawn students' submission IDs and removing from AcP  
using AcP as master list to determine corpus  
```{r}

rm.withdrawals = function(df, stud.col, course.col, sem.col) {
  new.col = dim(df)[2] + 1
  df[,new.col] = 0
  df = rename(df, new.col, "UniqueID")
  for (i in 1:nrow(df)) {
        df[i,new.col] = paste0(df[i,stud.col], df[i,course.col], df[i,sem.col])
  }
  if (length(which(df[,new.col] %in% w)) > 0) {
    df2 = df[-rev(which(df[,new.col] %in% w)),]
  }
  else {df2 = df}
  return(df2)
}


AcP.biol.wo.withdrawn = rm.withdrawals(AcP.biol.df, 1, 22, 23)
AcP.biom.wo.withdrawn = rm.withdrawals(AcP.biom.df, 1, 21, 22)

#SubID.StudID.AcP.biol.wo.withdrawn = AcP.biol.wo.withdrawn[,c(2,1)]
#SubID.StudID.AcP.biom.wo.withdrawn = AcP.biom.wo.withdrawn[,c(2,1)]

SubID.master = c(AcP.biol.wo.withdrawn[,2], AcP.biom.wo.withdrawn[,2])
#length(unique(SubID.master))

df = AcP.biol.df
#length(which(df[,2] %in% SubID.master))
df.fixed = df %>% filter(SubmissionID %in% SubID.master) 
AcP.biol.df = df.fixed

df = AcP.biom.df
#length(which(df[,2] %in% SubID.master))
df.fixed = df %>% filter(SubmissionID %in% SubID.master) 
AcP.biom.df = df.fixed

```


identifying students who repeated or did both courses  
(doesn't change corpus, just identifies students in case of duplication problems later)  
```{r}

df = demog.df
dup.studs = dup(df, 1, 1)
dup.studs.df = df %>% filter(StudentID %in% dup.studs)
dup.studs.tally = dup.studs.df %>% group_by(StudentID, course) %>% tally(sort = TRUE)

table(dup.studs.tally$n)
filter(dup.studs.tally, n >= 2) 

studs.rep = filter(dup.studs.tally, n >= 2) 
studs.rep.biol = as.data.frame(filter(studs.rep, course == "BIOL1040") %>% select(StudentID))
studs.rep.biom = as.data.frame(filter(studs.rep, course == "BIOM2011") %>% select(StudentID))
studs.both.courses = as.data.frame(filter(dup.studs.tally, n == 1) %>% select(StudentID))
studs.both.courses = unique(studs.both.courses)

```


*removing remarks and withdrawn from FbP and FbU*   
```{r}
df = FbP.df
#names(df)
df.fixed = df %>% filter(SubmissionID %in% SubID.master) 
FbP.df = df.fixed

df = FbU.df
#names(df)
df.fixed = df %>% filter(SubmissionID %in% SubID.master) 
FbU.df = df.fixed

```


##FbP errors  
found audio annotations where Duration.sec was NA ie did not upload to server from iPad properly  
```{r}
#NB found error - 45 audio files have NA for duration
FbP.audio.missing = subset(FbP.df, AnnotType == "Recording" & is.na(Duration.sec))
r = rownames(FbP.audio.missing)
FbP.audio.missing[r[1:3],]
FbP.df[r[1:3],]
r = as.numeric(r)
df = FbP.df[-r,]
#check to see correct rows removed
subset(df, AnnotType == "Recording" & is.na(Duration.sec)) 

FbP.df = df
```


found duplicates for all columns in FbP.df
```{r}

dups = which(duplicated(FbP.df))
df = FbP.df[-dups,]
nrow(FbP.df) - nrow(df)
length(dups)
which(duplicated(df)) #check
FbP.df = df

#checking other data sets
dups = which(duplicated(FbU.df))
length(dups)

dups = which(duplicated(AcP.biol.df))
length(dups)

dups = which(duplicated(AcP.biom.df))
length(dups)

```

#FbU transformations  
changing audio filenames to match FbP  
```{r}
df = FbU.df
df$Filename[1:5]
df$Filename = gsub(".mp3", ".m4a", df$Filename)
df$Filename[1:5]
FbU.df = df
```

converting msecB4scroll to sec and minute  
```{r}
df = FbU.df %>% mutate(pause.sec = msec.B4.scroll/1000)
df = df %>% mutate(pause.min = msec.B4.scroll/(1000*60))
FbU.df = df
```

#AcP transformations  
fixing marks for biol  
```{r}
df = AcP.biol.df
head(df)
df = df.mark.convert(df, 5, 16)

missing = which(is.na(df[,18]))
df[missing[1:5],c(5:16,18)]
for (i in 1:length(missing))
  df[missing[i],18] = round((sum(df[missing[i],5:16])/12),0)
df[missing[1:5],c(5:16,18)]

df = df.mark.convert(df, 18, 18)

new.cols = c(length(df) + 1, length(df) + 2) 
df[,new.cols] = 0
df = rename(df, new.cols, c("Final.Grade.calc", "Final.Grade.percent"))

table(df[,8])
summary(df[,new.cols])

for (i in 1:nrow(df)) {
  if(df[i,21] == "BIOL1040Sem1Report 0") {
    df[i,8] = as.numeric("")
    df[i,new.cols[1]] = round((sum(df[i,c(5:7,9:16)])/11),0)
    df[i,new.cols[2]] = round(((sum(df[i,c(5:7,9:16)])/44)*100),0)
  }
  else {
    df[i,new.cols[1]] = round((sum(df[i,5:16])/12),0)
    df[i,new.cols[2]] = round(((sum(df[i,5:16])/48)*100),0)
  }
}

summary(df[,new.cols])

AcP.biol.df = df

```


#FbP transformations  
adding word count variable  
```{r}

df = FbP.df
new.col = length(df) + 1
df[,new.col] = 0
df = rename(df, new.col, "WordCount")

annot.type.col = 4
annot.col = 11

for (i in 1:nrow(df))
  if (df[i,annot.type.col] == "Text")
      df[i,new.col] = sapply(gregexpr("\\W+", df[i,annot.col]), length)

#adding word count for audio annotations
annot.col = 12

for (i in 1:nrow(df))
    if (df[i,annot.type.col] == "Recording")
      df[i,new.col] = round(df[i,annot.col]*(164/60),0)

#df[1:6,c(annot.col,annot.type.col,new.col)]

FbP.df = df

```



#summarising  
#AcP  
combining biol and biom  
```{r}

df = AcP.biol.df[,c(1:4, 26, 21:24)]
df = rename(df, 5, "Final.Grade")
AcP.df = rbind(df, AcP.biom.df[,c(1:4, 19:23)])

```


#FbU  
open duration and bins, and merging w AcP  
```{r}
open.dur = summarise(FbU.df, 15, 60000, 2, "OpenDuration.min")
bins = c(0, 1, 60, 4600)
df = open.dur
df$open.bin = cut(df[,2], bins)
df[1:5,]
levels(df[,3]) = c("short", "medium", "long")
table(df[,3])
open.dur = df

df = NULL
df = merge(AcP.df, open.dur, by="SubmissionID", all.x=T, all.y=F)

df[1:5,]
col = 11
#summary(df[,col])
unopened = which(is.na(df[,col]))
df[,col] = as.character(df[,col])
df[unopened,col] = "unopened"
df[,col] = as.factor(df[,col])

AcP.open.bins = df

#open.dur[1:5,]
```

adding in final vs nonfinal categorisation  
```{r}
# for AcP.open.bins
df = AcP.open.bins %>% filter(report != "Report 0" & report != "Report 1" & project != "BIOL1040Sem1Report 2" & project != "BIOL1040Sem2Report 2")

finalsub = df[,1]

AcP.open.bins$final = "nonfinal"
AcP.open.bins$final[which(AcP.open.bins$SubmissionID %in% finalsub)] = "final"
head(AcP.open.bins)
tail(AcP.open.bins)

# for FbU
finalsub = AcP.open.bins %>% filter(final == "final") 
FbU.df$final = "nonfinal"
FbU.df$final[which(FbU.df$SubmissionID %in% finalsub$SubmissionID)] = "final"

```

#FbP  
sum of annotations per submission ID  
```{r}
df = FbP.df
df2 = table(df[,1], df[,4])
df3 = as.data.frame(df2[,1])
for (i in 2:ncol(df2))
  df3 = cbind(df3, df2[,i])
df3 = rename(df3, 1:4, colnames(df2))
SubmissionID = rownames(df2)
df3 = cbind(SubmissionID, df3)
annot.num = df3
annot.num[1:5,]

audio.dur = summarise(FbP.df, 12, 60, 1, "auidio.min")

annot.length.audio = summarise(subset(FbP.df, AnnotType == "Recording"), 18, 1, 1, "audio.words")
annot.length.txt = summarise(subset(FbP.df, AnnotType == "Text"), 18, 1, 1, "txt.words")
annot.length = summarise(FbP.df, 18, 1, 1, "total.words")

audio.dur[1:5,]
annot.length.audio[1:5,]
annot.length.txt[1:5,]
annot.length[1:5,]

FbP.summary = merge(annot.num, annot.length, by="SubmissionID")
FbP.summary = merge(FbP.summary, audio.dur, by="SubmissionID", all.x=T)
FbP.summary = merge(FbP.summary, annot.length.audio, by="SubmissionID", all.x=T)
FbP.summary = merge(FbP.summary, annot.length.txt, by="SubmissionID", all.x=T)

FbP.summary[1:5,]
FbP.summary[which(FbP.summary[,1] == 1486),]

```

FbP.summary fix?  
*not sure what this is...*  
```{r}
df = FbP.summary

x = NULL
for (i in 1:5)
  x[i] = df$total.word[[i]]
x

length(which(is.na(df[,8])))
#x = which(is.na(FbP.summary[,8]))


#df[1:5,]
col = 8
#summary(df[,col])
none = which(is.na(df[,col]))
#df[,col] = as.character(df[,col])
df[none,col] = 0

col = 9
none = which(is.na(df[,col]))
df[none,col] = 0
df[1:6,]

str(df[,1])
df[,1] = as.character(df[,1])
df[,1] = as.numeric(df[,1])
FbP.summary = df

```


merging audio provision with audio use
```{r}
#working out which variables are important in finding duplicates
#including x and y locations (ie some annotations might be used more than once on a page)
FbP.audio = subset(FbP.df, AnnotType == "Recording")
which(duplicated(FbP.df))
which(duplicated(FbP.audio))
FbP.audio = FbP.audio[,c(1,2,5:7,10,12,14:17)]
which(duplicated(FbP.audio))
df = FbP.audio[which(duplicated(FbP.audio)), 6]
length(df)
df2 = FbP.audio %>% filter(Filename %in% df)
nrow(df2)
df3 = FbP.df %>% filter(Filename %in% df)
nrow(df3)
df4 = FbU.df %>% filter(Filename %in% df)
nrow(df4)

#but can't work out if student played both or 1 annot twice eg
FbP.df[which(FbP.df[,10] == df[1]),]
FbU.df[which(FbU.df[,20] == df[1]),]
#and this presents issues later for merge, so need to remove all duplicate filenames

#missing x and y locations
FbP.audio = subset(FbP.df, AnnotType == "Recording")
which(duplicated(FbP.df))
which(duplicated(FbP.audio))
FbP.audio = FbP.audio[,c(1,2,5,10,12,14:17)]
which(duplicated(FbP.audio))
df = dup(FbP.audio, 4, 4)
length(df)
df2 = FbP.audio %>% filter(Filename %in% df)
nrow(df2)
df3 = FbP.df %>% filter(Filename %in% df)
nrow(df3)
df4 = FbU.df %>% filter(Filename %in% df)
nrow(df4)


#removing the duplicated audio filenames - will still see if then filename was used by students
df.fixed = FbP.df
for (i in 1:length(df))
  df.fixed = df.fixed[-(which(df.fixed$Filename == df[i])),]
nrow(FbP.df)
nrow(df.fixed)
nrow(FbP.df) - nrow(df.fixed)
FbP.df = df.fixed

FbP.audio = subset(FbP.df, AnnotType == "Recording")
FbP.audio = FbP.audio[,c(1,2,5:7,10,12,14:17)]
which(duplicated(FbP.audio)) #check

FbU.audio = subset(FbU.df, Interaction == "Audio")
FbU.audio = FbU.audio[,c(1,10,16:20)]
which(duplicated(FbU.audio)) #check

nrow(FbP.audio)
nrow(FbU.audio)
FbP.FbU.audio = merge(FbP.audio, FbU.audio, by="Filename", all.x=T)
#nrow(FbP.FbU.audio)
#length(unique(FbP.FbU.audio$EventID))
#summary(FbP.FbU.audio)
#checkig if all EventIDs are unique - need to remove NAs
df2 = remover(FbP.FbU.audio, 12)
nrow(df2)
length(unique(df2$EventID))
length(which(duplicated(df2$EventID)))

#adding category for FbP audio that were unused in FbU
unused = which(is.na(FbP.FbU.audio$EventID))
unused.filename = FbP.FbU.audio[unused,1]
u = unused.filename[1:10]
FbP.audio %>% filter(Filename %in% u)

df = FbP.FbU.audio
df[unused,13] = "unused"
summary(df)
df[1:20,]
addmargins(table(df[,13]))

nrow(df)

FbP.FbU.audio = df

with(FbP.FbU.audio, addmargins(table(project, State)))
with(FbP.FbU.audio, addmargins(prop.table(table(project, State),1)))

audio.use = as.data.frame(table(FbP.FbU.audio$Filename, FbP.FbU.audio$State))
audio.use[1:5,]
names(audio.use) = c("Filename", "State", "Freq")

audio.files = FbP.FbU.audio[,c(1:11)]
audio.files = unique(audio.files)
which(duplicated(audio.files$Filename))
nrow(audio.use)
nrow(audio.files)
audio.use = merge(audio.use, audio.files, by="Filename")
nrow(audio.use)

audio.use[1:5,]
length(unique(audio.use$SubmissionID))
length(unique(audio.use$Filename))

audio.use[which(audio.use$SubmissionID == 1486),]
length(which(audio.use$SubmissionID == 1486))
length(unique(audio.use[which(audio.use$SubmissionID == 1486),1]))

FbP.summary[which(FbP.summary$SubmissionID == 1486),]

```

summary of proportion of audios used and not used
```{r}
names(audio.use)

#number of submissions
a = unique(audio.use[,c(4,11,13)])
dcast(a, course ~ report)

#number of audio annotations
a = unique(audio.use[,c(1,4,11,13)])
dcast(a, course ~ report)

#number of audio in each state for each course and report
a = audio.use[,c(11,13,2,3)]
acast(a, course ~ report ~ State, sum)

#this gives the same result
with(FbP.FbU.audio, addmargins(table(project, State)))
with(FbP.FbU.audio, addmargins(prop.table(table(project, State),1)))

nrow(audio.use)
t1 = audio.use %>% filter(Freq > 0)
t2 = dcast(t1, SubmissionID+Filename~State, value.var="Freq", fun.aggregate=sum)
#t4a = dcast(t1, SubmissionID+Filename~State, value.var="Freq", fun.aggregate=sum, margins = T)
head(t2,n=15)
t2 = as.data.frame(t2)

t3 = t2[,1:2]
for (i in 1:nrow(t2)){
  for (j in 3:6) {
    t3[i,j] = as.numeric(t2[i,j] > 0)
  }
}
names(t3) = names(t2)
head(t3, n=15)

t3m = melt(t3, id=c("SubmissionID", "Filename"))
head(t3m, n=15)

t4 = dcast(t3m, SubmissionID ~ variable, fun.aggregate = sum)
head(t4, n=15)


#number of audio annots per submission ID
totals = t3 %>% group_by(SubmissionID) %>% tally()
head(totals, n=15)

t5 = merge(t4, totals, by="SubmissionID")
t5 = rename(t5, 6, "Recording")

t5 = t5 %>% mutate(finished.p = round((finished/Recording)*100),0)
t5 = t5 %>% mutate(pause.p = round((pause/Recording)*100),0)
t5 = t5 %>% mutate(scrubbed.p = round((scrubbed/Recording)*100),0)
t5 = t5 %>% mutate(unused.p = round((unused/Recording)*100),0)
head(t5, n=15)

#checker
t = t5
t[which(t$SubmissionID == 1501),]

audio.use.sum = as.data.frame(t5)

#adding iv back in

df = audio.use.sum
names(df)
df.fixed = df %>% filter(SubmissionID %in% SubID.master) 
#audio.use.sum = df.fixed

df = audio.use
names(df)
df.fixed = df %>% filter(SubmissionID %in% SubID.master) 
#audio.use = df.fixed

df = merge(audio.use.sum, audio.use[,c(4,10:13)], by="SubmissionID", all.x = T, all.y = F)
#dim(unique(df))
df = unique(df)
head(df)
audio.use.sum = df

```

audios played more than once  
```{r}

t3 = t2[,1:2]
for (i in 1:nrow(t2)){
  for (j in 3:6) {
    t3[i,j] = as.numeric(t2[i,j] > 1)
  }
}
names(t3) = names(t2)
head(t3, n=15)

t3m = melt(t3, id=c("SubmissionID", "Filename"))
head(t3m, n=15)

t4 = dcast(t3m, SubmissionID ~ variable, fun.aggregate = sum)
head(t4, n=15)

t5 = merge(t4, totals, by="SubmissionID")
t5 = rename(t5, 6, "Recording")

t5 = t5 %>% mutate(finished.p = round((finished/Recording)*100),0)
t5 = t5 %>% mutate(pause.p = round((pause/Recording)*100),0)
t5 = t5 %>% mutate(scrubbed.p = round((scrubbed/Recording)*100),0)
t5 = t5 %>% mutate(unused.p = round((unused/Recording)*100),0)
head(t5, n=15)

audio.use_multiple.sum = as.data.frame(t5)

df = merge(audio.use_multiple.sum, audio.use.sum[,c(1,11:14)], by="SubmissionID")
head(df)
audio.use_multiple.sum = df

```

SubmissionID index used to differentiate by course etc  
(determined using AcP as the defining list of corpus)  
```{r}
SubID.index = AcP.df[,c(2,1,6:9)]
```

writing  
```{r}

folder = "./Data Stage 2/"
write.csv(demog.df, file=paste0(folder, "demog.csv"), row.names=FALSE)

write.csv(AcP.biol.df, file=paste0(folder, "AcPbioldf.csv"), row.names=FALSE)
write.csv(AcP.biom.df, file=paste0(folder, "AcPbiomdf.csv"), row.names=FALSE)
write.csv(AcP.df, file=paste0(folder, "AcPdf.csv"), row.names=FALSE)
write.csv(AcP.open.bins, file=paste0(folder, "AcPFbUbins.csv"), row.names=FALSE)

write.csv(FbP.df, file=paste0(folder, "FbPdf.csv"), row.names=FALSE)
write.csv(FbP.summary, file=paste0(folder, "FbPsummary.csv"), row.names=FALSE)

write.csv(FbU.df, file=paste0(folder, "FbUdf.csv"), row.names=FALSE)

write.csv(audio.use, file=paste0(folder, "AudioUse.csv"), row.names=TRUE)
write.csv(audio.use.sum, file=paste0(folder, "AudioUseSummary.csv"), row.names=FALSE)
write.csv(audio.use_multiple.sum, file=paste0(folder, "AudioUseManySummary.csv"), row.names=FALSE)

write.csv(SubID.index, file=paste0(folder, "SubIDindex.csv"), row.names=FALSE)

write.csv(studs.withdrew, file=paste0(folder, "withdrawals.csv"), row.names=FALSE)
write.csv(remarks.subID, file=paste0(folder, "remarks.csv"), row.names=FALSE)

```




