---
title: "UQM paper - audio use"
author: "KZ"
date: "10 July 2015"
output: html_document
---

A few quick outputs  

*_NB all adjusted so that the 'unopened' reports are not included in calculating proportion of audio used_*
```{r, echo=FALSE, message=FALSE, warning=FALSE}
#clean workspace
rm(list=ls())

#packages
require(reshape2)
require(dplyr)

#scripts
source("UQM functions.R")
source("HelperFunctions.R")

#data
folder = "./Data Stage 2/"

audio.use = read.csv(paste0(folder, "AudioUse.csv"), header=TRUE, stringsAsFactors=FALSE)
audio.sum = read.csv(paste0(folder, "AudioUseSummary.csv"), header=TRUE, stringsAsFactors=FALSE)
audio.sum.many = read.csv(paste0(folder, "AudioUseManySummary.csv"), header=TRUE, stringsAsFactors=FALSE)
FbPsum = read.csv(paste0(folder, "FbPsummary.csv"), header=TRUE, stringsAsFactors=FALSE)
AcPFbUbins = read.csv(paste0(folder, "AcPFbUbins.csv"), header=TRUE, stringsAsFactors=FALSE)


#setup
ProjectID = read.csv("./Data Stage 1/ProjectIDs.csv")
projects()
graphs()

#checking data
sub = subset(AcPFbUbins, open.bin == "unopened")
sub = sub[,1]
#length(which(audio.use$SubmissionID %in% sub))
#length(which(audio.sum$SubmissionID %in% sub))

au = audio.use
as = audio.sum
am = audio.sum.many

unused = which(audio.use$SubmissionID %in% sub)
audio.use = audio.use[-unused,]

unused = which(audio.sum$SubmissionID %in% sub)
audio.sum = audio.sum[-unused,]

unused = which(audio.sum.many$SubmissionID %in% sub)
audio.sum.many = audio.sum.many[-unused,]


```

##proportion of all audio annotations (per report set) that were played in full at least once  
```{r, echo=FALSE, fig.width=10, fig.height=5}

df = audio.use
#names(df)
t = NULL
t2 = NULL
ls = split(df, df$project)
for (l in 1:length(ls)) {
  df = ls[[l]]
  t[[l]] = tapply(df$Freq, df$State, sum)
  t2[[l]] = as.data.frame(addmargins(prop.table(t[[l]])))
}
#t
#t2
names(t2) = names(ls)
df2 = ls.df(t2,0)
df2 = rename(df2, 1, "audio.use")
df2$audio.use = round(df2$audio.use*100,0)
df2$State = rownames(df2)
df2$State = gsub("[[:digit:]]", "", df2$State)
rownames(df2) = 1:nrow(df2)
df2 = df2[,c(6,1:5)]
#head(df2, n=15)
df3 = subset(df2, State == "finished")

default.plot()
par(mar = c(5.1, 5.0, 4.1, 2.1))
barplot(df3$audio.use, names = report.names, las=2, col=report.col, ylim=c(0,100), ylab="Proportion of audio annotations played \n(% of audio annotations across all reports)", axis.lty=1.0)
legend.top(sem.names,  kz.col)

```

##proportion of audio annotations (in each report) that were played in full at least once  
```{r, echo=FALSE, fig.width=10, fig.height=5}

df = audio.sum
#names(df)

default.plot()
par(mar = c(5.1, 5.0, 4.1, 2.1))
plot.mean.sem(df, 7, 11, 100, report.col, report.names, "Proportion of audio annotations played \n(% per report)")
legend.top(sem.names,  kz.col)

temp = as.data.frame(table(df[,12], df[,14]))

```



##proportion of audio annotations (in each report) that were played in full more than once  
```{r, echo=FALSE, fig.width=10, fig.height=5}

df = audio.sum.many
#names(df)

default.plot()
par(mar = c(5.1, 5.0, 4.1, 2.1))
plot.mean.sem(df, 7, 11, 100, report.col, report.names, "Proportion of audio annotations \nplayed multiple times (% per report)")
legend.top(sem.names,  kz.col)

temp = as.data.frame(table(df[,12], df[,14]))

```

